Disc stuff

### 2012-09-21 paper.tex
added some figs to paper

 \caption{enevlope model}
\end{figure}

@@

-describe the physical structure of the disk (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
The physical strucure of the disc is the same as the one used in Ilee et al. (2011), based on the work of Boley(2007), Boley \& Durisen(2008) and Boley(2009). This model describes a 0.39$\,rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms. Densities in the disc range from 10$^{10}$-10$^{21}\,\rm{m}^{-3}$, and temperatures range from 30-400 K. The model is sampled over a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$au in x, y and z. The majority of the mass lies in the midplane of the disc.\newline

@@

-describe the RT used (LIME) 
LIME, the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continous 3d model. The method of selecting these points is given in the gridding section. At each of these points the density of the main collision partner (in this case H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity and taken from the model. These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the vairiation in distance between points whilst keeping the same underlying distribution. These points are then connected by Delaunay triangulation and it is down these paths that photons are restricted to propagating. The levels of molecules in question are then  calculated at each of these points from collional and radiative (de)excitation and the local radiation field is calculated. This is repeated 20 times with the populations of each level converging towards a single value.
 Dust opacities used\newline

-how did you build the grid  (if this is too long it can go in an appendix)  - figure with the grid

@@

\begin{figure}
 \includegraphics[width=84mm]{Figures/model/lime_points_rz.png}

@@

Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmicly spaced in r. For each point to be selected a random number [0-1), $\alpha$ is generated as a threshold. After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compaired against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$). If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r,$\phi$,z co-ordinte is selected. The weighting function and gridding functions were selected empiricly to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest. 20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
In addiation to this method of selection 5\% of the points are randomly distributed about the model with no bias with regards to density or abundance. This provides a minimum level of sampling for the large low density regions in the outer regions of the simulated volume.

@@

Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first])  
Figure showing different inclinations  
Figure showing different transitions of the same molecule (e.g. CO(1-0), ...(7-6) , OCS,  H2CO ) for same inclination but in different disks (Boley et al. and the smooth disk)

@@

note that all speices show up in absorption and some show a little bit of emission around the edges of the disc
OCS is good for showing up spiral structure
enevelope only contaminates the central plusminus 500 m/s or so

>>>>

 \caption{enevlope model with temp and dust temp (red, green) in kelvin, log number density (blue) in cm$^{-1}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$}
\end{figure}

@@

-describe the physical structure of the disk (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
The physical strucure of the disc is the same as the one used in Ilee et al. (2011), based on the work of Boley(2007), Boley \& Durisen(2008) and Boley(2009). This model describes a 0.39$\,rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms. Densities in the disc range from 10$^{10}$-10$^{21}\,\rm{m}^{-3}$, and temperatures range from 30-400 K. The dust and gas temperatures in the disc are assumed to be equal. The gas/dust mass ratio was assumed to be 1/100 throughout the model and the opacities were given by the model of dust grains with thick icy mantles and 10$^6\,$yr coagulation from Ossenkopf and Henning (1994). The model is sampled over a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$au in x, y and z. The majority of the mass lies in the midplane of the disc.\newline

@@

-describe the RT used (LIME) 
LIME, the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continous 3d model. The method of selecting these points is given in the gridding section. At each of these points the density of the main collision partner (in this case H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity and taken from the model. These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the vairiation in distance between points whilst keeping the same underlying distribution. These points are then connected by Delaunay triangulation and it is down these paths that photons are restricted to propagating. The levels of molecules in question are then  calculated at each of these points from collional and radiative (de)excitation and the local radiation field is calculated. This is repeated 20 times with the populations of each level converging towards a single value. \newline

@@

\begin{figure}
 \includegraphics[width=84mm]{Figures/model/lime_points_rz2.png}

@@

In order to construct the grid, points are randomly selected from the volume being simulated then compaired against a reference point. Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmicly spaced in r. For each point to be selected a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold. After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compaired against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$). If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r,$\phi$,z co-ordinte is selected. The weighting function and gridding functions were selected empiricly to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest. 20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled. In addiation to this method of selection 5\% of the points are lineraly distributed in x, y and z with no bias with regards to density or abundance. This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume. See figure 5 for example of the points distribution in r, z.

@@

Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first]) (Note the moment 1 and 0 map were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in the some PV diagrams as the strong absorption feature at all positions around zero velocity, mom1maps are shown with a cutoff of 1/1000 of the peak emission/apsorption value)
\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}

 \caption{CO 3-2 Continuum subtracted mom0}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_mom1.png}

 \caption{CO 3-2 mom1map}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_PV_centre.png}

 \caption{CO 3-2 PV through centre}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_contSub.png}

 \caption{OCS 28-27 Continuum subtracted mom0}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_mom1.png}

 \caption{OCS 28-27 mom1map}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_PV_centre.png}

 \caption{OCS 28-27 PV through centre}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4->3-0-3_30deg_contSub.png}

 \caption{H$_2$CO 4$\,$0$\,$4 - 3$\,$0$\,$3 Continuum subtracted mom0}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4->3-0-3_30deg_mom1.png}

 \caption{H$_2$CO 4$\,$0$\,$4 - 3$\,$0$\,$3 mom1map}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4->3-0-3_30deg_PV_centre.png}

 \caption{H$_2$CO 4$\,$0$\,$4 - 3$\,$0$\,$3 PV through centre}
\end{figure}

Figure showing different inclinations  
Figure showing different transitions of the same molecule (e.g. CO(1-0), ...(7-6) , OCS,  H2CO ) for same inclination but in different disks (Boley et al. and the smooth disk)

@@

note that all speices show up in absorption and some show a little bit of emission around the edges of the disc
OCS is good for showing up spiral structure without being able to resolve it.
enevelope only contaminates the central plusminus 500 m/s or so
